\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-06 paper.qmd
Updated Figure 18 title

```{r}
#| label: fig-model-error-mnist
#| fig-cap: "(a) The $10\\text{-}D$ model error for tSNE layout in $\\gD{}$ of MNIST digit 1 dataset. Most low $10\\text{-}D$ model errors are distributed along the big non-linear clutser, while most large $10\\text{-}D$ model errors are concentrated along the small cluster. (b) There are certain data points that exhibit large error rates due to their deviation from the usual $10\\text{-}D$ data structure, which makes them anomalies. These anomalies can be classified into two types: those that are anomalies within the non-linear structure and those that lie outside of it. The images associated with high model error points within the non-linear structure display different patterns of the digit 1. However, when comparing these images to the ones found outside of the non-linear structure, it becomes evident that the latter display different patterns of the digit 1 (c). "
#| fig-pos: H
#| fig-width: 4
#| fig-height: 8
#| out-height: 80%

error_plot_mnist / (imge_error_sample_within + imge_error_sample_outside) +
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag.position  = c(0.92, 0.92),
        plot.tag = element_text(color = "grey70"))
```

>>>>

```{r}
#| label: fig-model-error-mnist
#| fig-cap: "(a) The $10\\text{-}D$ model error for tSNE layout in $\\gD{}$ of the MNIST digit 1 dataset. Most low model errors are distributed along the big non-linear clutser, while most large model errors are concentrated along the small cluster. (b) There are certain images that exhibit large errors due to their deviation from the non-linear cluster, which makes them anomalies. The images associated with large model errors shows different patterns of digit 1."
#| fig-pos: H
#| fig-width: 4
#| fig-height: 8
#| out-height: 80%

#imge_error_sample_within

error_plot_mnist / (imge_error_sample_outside) +
  plot_annotation(tag_levels = 'a') &
  theme(plot.tag.position  = c(0.92, 0.92),
        plot.tag = element_text(color = "grey70"))
```

<!-- These anomalies can be classified into two types: those that are anomalies within the non-linear cluster and those that lie in the small cluster. The images associated with large model error points within the non-linear cluster display different patterns of the digit 1.  -->

### 2024-09-06 paper.tex
Updated Figure 18 title

\caption{\label{fig-model-error-mnist}(a) The \(10\text{-}D\) model
error for tSNE layout in \(\gD{}\) of MNIST digit 1 dataset. Most low
\(10\text{-}D\) model errors are distributed along the big non-linear
clutser, while most large \(10\text{-}D\) model errors are concentrated
along the small cluster. (b) There are certain data points that exhibit
large error rates due to their deviation from the usual \(10\text{-}D\)
data structure, which makes them anomalies. These anomalies can be
classified into two types: those that are anomalies within the
non-linear structure and those that lie outside of it. The images
associated with high model error points within the non-linear structure
display different patterns of the digit 1. However, when comparing these
images to the ones found outside of the non-linear structure, it becomes
evident that the latter display different patterns of the digit 1 (c).}

>>>>

\caption{\label{fig-model-error-mnist}(a) The \(10\text{-}D\) model
error for tSNE layout in \(\gD{}\) of the MNIST digit 1 dataset. Most
low model errors are distributed along the big non-linear clutser, while
most large model errors are concentrated along the small cluster. (b)
There are certain images that exhibit large errors due to their
deviation from the non-linear cluster, which makes them anomalies. The
images associated with large model errors shows different patterns of
digit 1.}
